---
title: "mzir"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview

`mzir` is an R package for plotting datasets from the Mach-Zehnder interferometric chemical sensor project.  Datasets are structured file folders in the following format:

```
dataset/            # Folder name is unimportant
  meta.json         # Stores metadata (chip ID, film ID, notes, etc.)
  intervals.csv     # Stores intervals data (time vs concentration)
  data.csv          # Raw interferometer output (time vs phase shift)
```

Data analysis consists of the following steps:

  #. Load and validate the dataset
  #. Adjust the intervals
  #. Align the intervals
  #. Fit the data within each interval to a model
  #. Sensitivity analysis
  #. Save processed results and plots
  

## Usage

`mzir` can be run in an interactive mode where it walks the user through the data analysis process, or as a regular R library.


## Tickets

- [x] create an `interval` class.
- [ ] create an `intervals` class.  This is a data frame that supports `nextElem.intervals()`.
- [ ] create a `dataset` class.  The dataset should have `data(dataset)` and `intervals(dataset)`.
- [ ] create `plot_interval(interval)`.
- [ ] create live-adjustable plots.
- [ ] create `fit_interval(interval)`

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
